Maximum Margin Matrix Factorization for Ensemble Clustering

### 2016-09-04 ensemble_clustering.tex
revise abs

\begin{abstract}
We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC). SFEC has capability to remove outliers of label assignments from multiple classifiers using a $\ell_{2,1}$ loss, which improves the performance of late fusion (large scale ability). To the best of our knowledge, this is the first work to connect ensemble clustering with late fusion. Compared to the state-of-the-art fusion algorithm, the SFEC achieves promising improvements on large scale dataset such as UCF101
%In this paper, we propose an efficient maximum margin matrix factorization algorithm for ensemble clustering.
%Our contributions include i) introduction of an efficient optimization for matrix completion based ensemble clustering methods; ii) an intuitive motivation for a $\ell_{1,2}$ loss.
%[Gao] , FM
\end{abstract}

@@

\subsection{Problem Formulation}{}
Suppose there are n testing instances, we denote each instance as a variable $x_i \belong R^d (1<=i<=n)$. Assuming we have already training m classifiers, $f_1(x), f_2(x), ... f_m(x)$, per classifier will predict a score vector $s_{ij}, 1<=i<=n, 1<=j<=m$，represent the result of j-th classifier on i-th testing instance. Our goal is to fusion these score vectors. Firstly, we transfer these score vectors to a label matrix P, each colums represent the highest value position of each instance. Then using label assigment, we convert multiple P matrixs into a 01 matrix L, see as{\ref{fig:framework}}. 
The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, which can be written as below
\begin{align}\label{eq:l12e}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
  \st        ~&~ \rank(\bX) \leq k  .
\end{align}
Problem~(\ref{eq:mc_l21}) is NP-hard due to the presence of the low rank constraint.
For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as
\begin{align}\label{eq:mf_l21}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
\end{align}
\noindent
Note that we have totally $K$ single clustering assignments.
Intuitively, we could set $k = K$ in Problem~(\ref{eq:mf_l21}).
Most existing matrix factorization optimization methods only consider smooth loss functions,
but the $\ell_{1,2}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently desccribed in the following section.

@@

\begin{table}[h]\small
\centering
\label{table:ucf101}
\begin{tabular}{c|c}
\hline
Method & Mean Accuracy(\%) \\\hline
SVM on Temporal Net Features & 86.2\% \\\hline
ASF &  86.8\% \\
MKL &  000 \\
RCEC &  000 \\
FWOT &  000 \\
LPBoost &  000 \\\hline
Ours &  000 \\
\hline
\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
\end{tabular}
\end{table}

>>>>

\begin{abstract}
% First: A big picture of the scenario which we would consider
In many real world applications, data can be represented in multiple ways/features, which would describe various characteristics of data.
Many works have shown that it could often improve the performance to make use of these features together.
% Second: what BIG problem would we like to solve?
Late fusion, which combines the predictions of multiple features, is a commonly used approach to generate the final decision for a test instance.
% Third: specify the detailed problem: find a precise position for our paper
However, it is ubiquitous that different features would dispute on some data, leading to the requirement of outlier rejection for late fusion algorithms.
% Fourth: general introduction of our method
In this paper, we propose an efficient matrix factorization based approach to fuse predictions from multiple sources, which could
relieve the performance degeneration caused by the controversy of multiple features on test data.
% Some unvalued sentence(s)
Extensive experiments demonstrate that the proposed method is effective to remove outliers and improve fusion performance.
% Written by DXY:
%We formulate the late score fusion algorithm as ensemble clustering problem, and propose an efficient optimization algorithm, namely Score Fusion via Ensemble Cluster(SFEC). SFEC has capability to remove outliers of label assignments from multiple classifiers using a $\ell_{2,1}$ loss, which improves the performance of late fusion (large scale ability). To the best of our knowledge, this is the first work to connect ensemble clustering with late fusion. Compared to the state-of-the-art fusion algorithm, the SFEC achieves promising improvements on large scale dataset such as UCF101
\end{abstract}

@@

\subsection{Problem Formulation}{}
Suppose there are n testing instances, we denote each instance as a variable $x_i \in \dsR^d (1<=i<=n)$. Assuming we have already training m classifiers, $f_1(x), f_2(x), ... f_m(x)$, per classifier will predict a score vector $s_{ij}, 1<=i<=n, 1<=j<=m$，represent the result of j-th classifier on i-th testing instance. Our goal is to fusion these score vectors. Firstly, we transfer these score vectors to a label matrix P, each colums represent the highest value position of each instance. Then using label assigment, we convert multiple P matrixs into a 01 matrix L, see as{\ref{fig:framework}}.
The core of our proposed algorithm is to apply $\ell_{1,2}$ to capture the outliers as well as anomalous columns in matrix L, which can be written as below
\begin{align}\label{eq:l12e}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
  \st        ~&~ \rank(\bX) \leq k  .
\end{align}
Problem~(\ref{eq:mc_l21}) is NP-hard due to the presence of the low rank constraint.
For the sake of efficiency on large scale matrices, we consider matrix factorization approaches to optimize it, which can be written as
\begin{align}\label{eq:mf_l21}
  \min_{\bX} ~&~ || \bL - \bX ||_{1,2}    \nonumber \\
  \st        ~&~ \bX = \bU \bV,~\bU \in \dsR^{N \times k},~\bV \in \dsR^{k \times MK} .
\end{align}
\noindent
Note that we have totally $K$ single clustering assignments.
Intuitively, we could set $k = K$ in Problem~(\ref{eq:mf_l21}).
Most existing matrix factorization optimization methods only consider smooth loss functions,
but the $\ell_{1,2}$ loss in Problem~(\ref{eq:mf_l21}) is nonsmooth.
we apply augmented Lagrangian multiplier (ALM) to optimize the nonsmooth objective function efficiently desccribed in the following section.

@@

\begin{table}[h]\small
\centering
\label{table:ucf101}
\begin{tabular}{c|c}
\hline
Method & Mean Accuracy(\%) \\\hline
SVM on Temporal Net Features & 86.2\% \\\hline
ASF &  86.8\% \\
MKL &  000 \\
RCEC &  000 \\
FWOT &  000 \\
LPBoost &  000 \\\hline
Ours &  000 \\
\hline
\end{tabular}
\caption{Mean Accuracy on UCF101 dataset for best single model and six fusion methods}
\end{table}
